Evaluating machine translation for assimilation via a gap-filling task

### 2015-04-05 2015-eamt-assim/2015-eamt-assim.tex
Fixed some more points from the reviews
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59621 72bbbca6-d526-0410-a7d9-f06f51895060

The evaluations took place online, in a system called Appraise \citep{federmann12}, which is 
designed specifically for various MT evaluation tasks. We adapted the code of Appraise to 
accommodate for the gap-filling tasks. The tasks were uploaded into the system and 
manually distributed between the participants by the following rules:
\begin{enumerate}
\item  Each participant evaluates every sentence (understood as a succession of words),
a total of 36;
\item  each participant evaluates 9 sentences in each of the four modes (see section~\ref{sec:methodology});
\item  all sentences of the set are evaluated with 10, 20 and 30\% of words removed;
\item each participant may encounter a given sentence in only one of the percentage variations;
\item  each sentence-mode-percentage combination is evaluated by more than one participant.
\end{enumerate}

>>>>

The evaluations took place online, in a system called Appraise \citep{federmann12}, which is 
designed specifically for various MT evaluation tasks. We adapted the code of Appraise to 
accommodate for the gap-filling tasks. The tasks were uploaded into the system and 
manually distributed between the participants by the following rules:
\begin{enumerate}
\item  Each participant evaluates every sentence (understood as a succession of words),
a total of 36;
\item  these sentences are divided into 4 groups of 9, one for each evaluation mode (see section~\ref{sec:methodology});
\item in total, all sentences of the set are evaluated with 10, 20 and 30\% of words removed;
\item each participant may encounter a given sentence in only one of the percentage variations;
\item  each sentence-mode-percentage combination is evaluated by more than one participant.
\end{enumerate}
